Kindly Bent to Free Us

### 2020-06-04 kindly/extensions.tex
Remove the misleading definition of lists.
subsection concurrency

\subsubsection{Algebraic Datatypes}

Algebraic data types are a staple of functional programming and fit nicely
in our paradigm. Indeed, it is sufficient to ensure  that the kinds of
the constructor arguments are less than or equal to the kind of the datatype.
Hence, it is forbidden to include affine elements in an unrestricted
datatype, whereas the elements in a linear list may be linear or
unrestricted. 
Here is the definition of a datatype for linear lists.

\begin{lstlisting}[numbers=none]
type ('a : 'k) llist : lin = Nil | Cons of ('a * 'a llist)
\end{lstlisting}

Our prototype implements non-recursive algebraic datatypes with
pattern matching.

\subsubsection{Branching constructs}

@@

>>>>

\subsubsection*{Algebraic Datatypes}

Algebraic data types are a staple of functional programming and fit nicely
in our paradigm. Indeed, it is sufficient to ensure  that the kinds of
the constructor arguments are less than or equal to the kind of the datatype.
Hence, it is forbidden to include affine elements in an unrestricted
datatype, whereas the elements in a linear list may be linear or
unrestricted.
Our prototype implements non-recursive algebraic datatypes with
pattern matching.

\subsubsection*{Branching constructs}

@@

\subsection{Concurrency}
\label{sec:concurrency}

While our present semantic model does not consider concurrency, some
design decisions were taken with a possible extension to concurrency
in mind. The main impact of this foresight is the distinction between
exclusive borrows and shared borrows, which materializes in the
metatheory. The intended contract of the shared 
borrow is that it can be duplicated and that the program consistently
observes the same state of the underlying resource inside its region
even in the presence of concurrency.

The exclusive borrow, on the other hand, is propagated according to
the evaluation order with the intention that any suspended binding
split of from an exclusive borrow has finished its action on the
resource before the borrow gets exercised. In the presence of
concurrency, this intended semantics of the exclusive borrow should
guarantee freedom of data races.

That is, if a thread closes over a borrow, that thread should have
terminated before the parent thread leaves the borrow's region. Rust
addresses this lifetime issue with the \lstinline/move/ qualification
for a thread which transfers ownership of the free variables to the
thread. However, moving (in Rust) only applies to the resource itself, but not
to borrows. A more discerning kind system would be needed for \lang to
enable safe sharing of synchronizable resources or borrows analogously
to Rust's \texttt{Sync} trait.
